Meta analysis of reprocessed RNASeq data from AMP-AD (all 6 brain regions)

### 2019-11-25 code/metaAnalysisForDiffExp_NoCBE.Rmd
Final Meta

## Store results in synapse
```{r syn.store, cache = FALSE, eval=FALSE, include=FALSE}
# Create folder to store results in synapse
CODE <- syn_temp$store(synapseclient$Folder(name = "MetaAnalysis", parentId = parentId))
Syns_Used <- c( 'syn8456631', 'syn8484996', 'syn8466814', 'syn21292041', 'syn21285564', 'syn21291908' )

>>>>

## Store results in synapse
```{r syn.store, cache = FALSE, eval=TRUE, include=FALSE}
# Create folder to store results in synapse
CODE <- syn_temp$store(synapseclient$Folder(name = "MetaAnalysis_NoCBE", parentId = parentId))
Syns_Used <- c( 'syn8456631', 'syn8484996', 'syn8466814', 'syn21292041', 'syn21285564', 'syn21291908' )
